---
title: "Homework 5"
author: "Mari Sanders"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(patchwork)
```

# Problem 1 

```{r}
bday_sim <- function(n) {
  bdays <- sample(1:365, size = n, replace = TRUE) 
  
  duplicate <- length(unique(bdays)) < n
  
  return(duplicate)
}

sim_res <- 
  expand_grid(
    n = 2:50, 
    iter = 1:10000
  ) %>% 
  mutate(res = map_lgl(n, bday_sim)) %>% 
  group_by(n) %>% 
  summarize(prob = mean(res))

sim_res %>% 
  ggplot(aes(x = n, y = prob)) + geom_line()
```

As the amount of people in the room increases, the probability that 2 people have the same birthday also increases. The probability that 2 people have the same birthday reaches 1 at around n = 50. This means if there are 50 people in the room, we are certain to have at least 2 people share a birthday. 

# Problem 2 

```{r}
ttest <- function(data) {
  t_test <- t.test(data) %>%  
    broom::tidy(t_test)
  return(t_test)
}

sim_results_df <- 
  expand_grid(
    true_mean = 0:6,
    iter = 1:5000
  ) %>% 
  mutate(
    estimate_df = map(true_mean, \(x) rnorm(30, x, 5)), 
    test = map(estimate_df, ttest)) %>% 
  unnest(test)

sim_results_df %>%
  group_by(true_mean) %>%
 mutate(prop = mean((p.value < .05))) %>%
  ggplot(aes(x = true_mean, y = prop)) +
  geom_line()

```

As the true mean increases, power increases. When `true_mean` equals to 6, the power goes to 1. 

```{r}
full_dataplot <- 
  sim_results_df %>% 
  group_by(true_mean) %>% 
  summarize(mean_estimate = mean(estimate, na.rm = TRUE)) %>% 
  ggplot(aes(x = true_mean, y = mean_estimate)) +  geom_line()

rejected_dataplot <-
  sim_results_df %>% 
  filter(p.value < 0.05) %>% 
  group_by(true_mean) %>% 
  summarize(mean_estimate = mean(estimate, na.rm = TRUE)) %>% 
  ggplot(aes(x = true_mean, y = mean_estimate))  + geom_line()

full_dataplot + rejected_dataplot
```

The plot across all samples shows that the average estimate $\hat \mu$ is approximately equal to $\mu$. The plot showing only when `p.value` is rejected seems to overestimate $\mu$ at lower `true_mean` values, but as the $\mu$ increases, the estimates become more accurate. 

# Problem 3 

```{r}
homicide_df <- read_csv("data/homicide-data.csv") %>% 
  unite(city_state, c(city, state), sep = ", ") %>% 
  mutate(result = ifelse(disposition == "Closed without arrest" | disposition == "Open/No arrest", "unsolved", "solved"))
```

This data has `nrow(homicide_df)` rows and `ncol(homicide_df)` columns. It includes the variables `names(homicide_df)`. To make the data easier to use, I combined the `city` and `state` variables in the original dataset to a single `city_state` column. In order to be able to calculate values needed in next questions, I made a column that outputted `unsolved` if `disposition` equaled Open/No Arrest or Closed Without Arrest and `solved` otherwise. 

```{r}
homicide_df %>% 
  group_by(city_state, result) %>% 
  summarize(count = n()) %>% 
  pivot_wider(
    names_from = "city_state",
    values_from = count
  ) %>% knitr::kable()
```

Baltimore Homicide Proportion

```{r}
baltimore_homicide <- 
  homicide_df  %>% 
  filter(city_state == "Baltimore, MD") %>% 
  group_by(result) %>% 
  summarize(count = n()) 

unsolved_count <- baltimore_homicide %>% 
  filter(result == "unsolved") %>% 
  pull(count)

total_count <- baltimore_homicide  %>% 
  summarize(total = sum(count)) %>% 
  pull(total)

broom::tidy(prop.test(unsolved_count, total_count)) %>% 
  select(estimate, conf.low, conf.high)
```

Other cities Homicide Proportion

```{r}
city_cases <- 
  homicide_df %>% 
  group_by(city_state, result) %>% 
  summarize(count = n())
city_counts <- city_cases %>%
  pivot_wider(names_from = result, values_from = count, values_fill = 0) %>%
  mutate(
    unsolved_count = unsolved,
    total_count = solved + unsolved
  )


results <- city_counts %>% 
  group_by(city_state) %>% 
  mutate(prop_test = map2(unsolved_count,total_count, \(x,y) prop.test(x = x, n = y )),
         tidy = map(prop_test, broom::tidy)) %>% 
  unnest(tidy) %>% select(city_state, estimate, conf.low, conf.high)

results %>% 
  ggplot(aes(x = fct_reorder(city_state, estimate), y = estimate)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + 
  labs(
    title = "Proportion of Unsolved Homicides by City",
    x = "City",
    y = "Estimated Proportion of Unsolved Homicides"
  )
```

